### 2023-10-26 manuscript.tex
Added discussion of simulation figure

\subsection{A model of constrained evolution reveals patterns of conserved features}
Though the BM process permits the inference of the rates of feature evolution after accounting for the phylogenetic relationships between species, it does not directly test for their conservation. In fact, under the BM model, trait variation is unconstrained and will increase without bound over time. Instead, evidence of conservation requires comparison to a model where trait variation is constrained. A common choice for modeling the effect of selection on the evolution of a continuous trait is the Ornstein-Uhlenbeck (OU) model. The OU model is similar to the BM model where a trait accumulates variation through a series of small, undirected steps. However, it differs in that the trait is also attracted towards an optimal value where the attraction is proportional to a parameter $\alpha$ and the trait's distance from this value. Under an additional assumption of stationarity that ensures parameter identifiability and estimate consistency, the OU model is therefore specified with three total parameters: the optimal value, the fluctuation magnitude, and the selection strength~\cite{Ho2013, Ho2014}. While the first two parameters are analogous to the root and rate parameters in the BM model, respectively, the selection strength has no equivalent.

% TODO: Add paragraph investigating statistical properties of hypothesis testing
% As both the BM and OU models are fully probabilistic, the data's relative support for the more complex OU model is quantified by the difference of its log-likelihood relative to that of the BM model. Because greater a log-likelihood indicates more support for a given model, a greater difference in log-likelihood indicates more support for the OU model over the BM model. However, to directly relate these differences to the probability of a type I error and to assess other statistical properties of the models under the hypothesis testing framework , we conducted a set of simulations.
% We simulated data under each model using the species tree and a range of parameter values. However, because the likelihood of a model is unchanged if the mean and observations are shifted by a constant, we fixed the mean and optimal values of the BM and OU models to zero during our simulations.
% Discuss estimations of model parameters when model is concordant with data generation process
%   - Make plots of mean estimates for both
%   - Re-scale OU heatmaps to calculate error
% This paragraph needs its own figure with panels for estimates of each model and type I/II error plots

>>>>

\subsection{A model of constrained evolution can identify conserved features}
Though the BM process permits the inference of the rates of feature evolution after accounting for the phylogenetic relationships between species, it does not directly test for their conservation. In fact, under the BM model, trait variation is unconstrained and will increase without bound over time. Instead, evidence of conservation requires comparison to a model where trait variation is constrained. A common choice for modeling the effect of selection on the evolution of a continuous trait is the Ornstein-Uhlenbeck (OU) model. The OU model is similar to the BM model where a trait accumulates variation through a series of small, undirected steps. However, it differs in that the trait is also attracted towards an optimal value where the attraction is proportional to the trait's distance from this value. Under an additional assumption of stationarity that ensures parameter identifiability and estimate consistency, the OU model is therefore specified with three total parameters: the optimal value ($\mu_{OU}$), the fluctuation magnitude ($\sigma^2_{OU}$), and the selection strength ($\alpha$)~\cite{Ho2013, Ho2014}. While the first two parameters are analogous to the root and rate parameters in the BM model, respectively, the selection strength has no equivalent.

As both models are fully probabilistic, the data's support for the OU model relative to the BM model is quantified by the log ratio of their likelihoods, with greater values indicating more support for the OU model. However, to empirically relate these values to type I and II error rates under a hypothesis testing framework and to assess other statistical properties of the models, we simulated data under each model with a range of values for each of its parameters. Because the likelihood of both models is unchanged if the mean and observations are shifted by a constant, we fixed the mean and optimal values of the BM and OU models to zero in our simulations.

The results show the rate of the BM model is accurately estimated over several orders of magnitude (Fig.~\ref{fig:simulation}A). Additionally, the variance of these estimates is proportional to the magnitude of the rate, indicated by the constant height of the violin plots in log scale. In contrast, the estimate of the rate of the OU model can have significant bias depending on relative values of the true parameters. For example, in the lower left, when $\log_{10}(\frac{\alpha}{\sigma^2_{OU}}) < 1$, $\sigma^2_{OU}$ is accurately estimated, as $\alpha$ is small relative to $\sigma^2_{OU}$~(Fig.~\ref{fig:simulation}B). In the central band, however, when $1 < \log_{10}(\frac{\alpha}{\sigma^2_{OU}}) < 3$, $\sigma^2_{OU}$, $\sigma^2_{OU}$ is overestimated, as some movement towards the optimal value is likely attributed to a greater fluctuation magnitude. Finally, in the upper right, when $\log_{10}(\frac{\alpha}{\sigma^2_{OU}}) > 3$, $\sigma^2_{OU}$ is underestimated, as movement from the restoring force overwhelms the contribution of the stochastic component. Similarly, the estimate of the selection strength is biased for many parameter value combinations, though the relationship is more complex~(Fig.~\ref{fig:simulation}C).
